maxent model avec xvalidation (year-based test training)

### 2019-04-11 src/maxent_avec_xvalidation.Rmd
minor alteration to make one-stop date change for running models

---
title: "maxent model avec xvalidation"
author: "Samantha Andrews"
output: html_notebook
---

@@

```{r pre-install & load packages, include=FALSE}
packages <- c("dismo", "stringr")
source("../src/ipak.R")
ipak(packages)
```

@@

jan variables to keep: temp_depth, salinty_depth, o2_depth, chl_surface, nao_sample, nao_winter 
```{r january data}
janprback <- subset(presback, month == "1")
janprback <- subset(janprback, select = c(occurrence, year, temp_depth, salinity_depth, o2_depth, chl_surface, nao_sample, nao_winter))
```

@@

```{r jan remove na vals}
janprback <- janprback[!is.na(janprback$temp_depth), ]
janprback <- janprback[!is.na(janprback$salinity_depth), ]
janprback <- janprback[!is.na(janprback$o2_depth), ]
janprback <- janprback[!is.na(janprback$chl_surface), ]
janprback <- janprback[!is.na(janprback$nao_sample), ]
janprback <- janprback[!is.na(janprback$nao_winter), ]
```

@@

```{r train and test on jan inc AIC for reg val}
mth <- "jan"
modelmonth <- cbind(paste0(mth ,unique(janprback$year)))
aicetc <- read.csv("../data/env/AICcCalculations.csv", header = TRUE) #pre-created csv file
betavallist <- cbind(aicetc$regularization)

for (year in 1:nrow(modelmonth)){
  timeslice <- modelmonth[year] #testing timeslice
  yr <- str_sub(timeslice, -4) #the year being used for testing
  train <- subset(janprback, year != yr) #training data is all years but testing
  trainpa <- train$occurrence #creates a vector of presence/background ID (1/0)
  test <-  subset(janprback, year == yr) #creates the testing dataset
  testp <- subset(test, occurrence == "1") #splits the testing dataset into presences
  testp <- subset(testp, select = -c(year, occurrence)) #don't need year and occurrence for modelling
  testb <- subset(test, occurrence == "0") #splits the testing dataset into background
  testb <- subset(testb, select = -c(year, occurrence)) #don't need year and occurrence for modelling
  train  <- subset(train, select = -c(year, occurrence)) #don't need year and occurrence for modelling

@@

```{r final models plus predict}
mth <- "jan"
modelmonth <- cbind(paste0(mth, unique(janprback$year)))
aicetc <- read.csv("../data/env/AICcFinalmod.csv", header = TRUE) #pre-created csv file
unlayer <- read.csv(paste0("../data/env/asc_layerlist", mth, ".csv"), header = TRUE) #if code doesnt work put back to unlayer_yr

for (year in 1:nrow(modelmonth)){
  timeslice <- modelmonth[year] #testing timeslice
  yr <- str_sub(timeslice, -4) #the year being used for testing
  train <- subset(janprback, year != yr) #training data is all years but testing
  trainpa <- train$occurrence #creates a vector of presence/background ID (1/0)
  test <-  subset(janprback, year == yr) #creates the testing dataset
  testp <- subset(test, occurrence == "1") #splits the testing dataset into presences
  testp <- subset(testp, select = -c(year, occurrence)) #don't need year and occurrence for modelling
  testb <- subset(test, occurrence == "0") #splits the testing dataset into background
  testb <- subset(testb, select = -c(year, occurrence)) #don't need year and occurrence for modelling
  train  <- subset(train, select = -c(year, occurrence)) #don't need year and occurrence for modelling

@@

    for (td in 1:nrow(unlayer_yr)){
      temp_depth <- raster(unlayer_yr$temp_depth[td])
      crs(temp_depth) <- "+proj=longlat +datum=WGS84 +ellps=WGS84 +towgs84=0,0,0" 
      names(temp_depth) <- "temp_depth"
      temp_depth <- projectRaster(temp_depth, aea)
      chl_surface <- raster(unlayer_yr$chl_surface[td])
      crs(chl_surface) <- "+proj=longlat +datum=WGS84 +ellps=WGS84 +towgs84=0,0,0" 
      names(chl_surface) <- "chl_surface"
      chl_surface <- projectRaster(chl_surface, aea)
      o2_depth <- raster(unlayer_yr$o2_depth[td])
      crs(o2_depth) <- "+proj=longlat +datum=WGS84 +ellps=WGS84 +towgs84=0,0,0" 
      names(o2_depth) <- "o2_depth"
      o2_depth <- projectRaster(o2_depth, aea)
      salinity_depth <- raster(unlayer_yr$salinity_depth[td])
      crs(salinity_depth) <- "+proj=longlat +datum=WGS84 +ellps=WGS84 +towgs84=0,0,0" 
      names(salinity_depth) <- "salinity_depth"
      salinity_depth <- projectRaster(salinity_depth, aea)
      nao_sample <- raster(unlayer_yr$nao_sample[td])
      crs(nao_sample) <- "+proj=longlat +datum=WGS84 +ellps=WGS84 +towgs84=0,0,0" 
      names(nao_sample) <- "nao_sample"
      nao_sample <- projectRaster(nao_sample, aea)
      nao_winter <- raster(unlayer_yr$nao_winter[td])
      crs(nao_winter) <- "+proj=longlat +datum=WGS84 +ellps=WGS84 +towgs84=0,0,0"
      names(nao_winter) <- "nao_winter"
      nao_winter <- projectRaster(nao_winter, aea)
      stackn <- unlayer_yr$stackname[td]
      stack <- stack(temp_depth, chl_surface, o2_depth, salinity_depth, nao_sample, nao_winter)
      #stackSave(test,unlayer_yr$stackname[td])
      pred <- predict(mod, stack, file = paste0("../output/maxent/predictions/", mth, "/", stackn, ".asc"), overwrite=TRUE) 
      prplot <- plot(pred, png(paste0("../output/maxent/predictions/", mth, "/", stackn, ".png"))) 
      dev.off() # stops automatic saving of the plot to a png
    }
}

stdep <- do.call(rbind, stackdeplst)
write.csv(stdep, paste0("../output/maxent/predictions/", mth, "/stack_depth.csv"), row.names = FALSE)
```

@@

```{r avg maxentReg}
#mth <- "jan"
#modelmonth <- cbind(paste0(mth, unique(janprback$year)))
for (i in 1:length(modelmonth)){
  timeslice <- modelmonth[i]
  yr <- str_sub(timeslice, -4) #the year being used for testing
  if(yr == 2003){
    aic2003 <- read.csv(paste0("../output/maxent/models/", timeslice, "/AICforMaxentReg.csv"), header = TRUE)
    } else if (yr == 2004){
    aic2004 <- read.csv(paste0("../output/maxent/models/", timeslice, "/AICforMaxentReg.csv"), header = TRUE)
    } else if (yr == 2005){
    aic2005 <- read.csv(paste0("../output/maxent/models/", timeslice, "/AICforMaxentReg.csv"), header = TRUE)
    } else if (yr == 2006){
    aic2006 <- read.csv(paste0("../output/maxent/models/", timeslice, "/AICforMaxentReg.csv"), header = TRUE)
  }
}

@@

write.csv(avgAIC, paste0("../output/maxent/models/", mth, "avgAIC.csv"), row.names = FALSE)
```

```{r avg maxres}
#mth <- "jan"
#modelmonth <- cbind(paste0(mth, unique(janprback$year)))
for (i in 1:length(modelmonth)){
  timeslice <- modelmonth[i]
  yr <- str_sub(timeslice, -4) #the year being used for testing
  if(yr == 2003){
    maxr2003 <- read.csv(paste0("../output/maxent/models/", timeslice, "/maxentResults.csv"), header = TRUE)
    } else if (yr == 2004){
    maxr2004 <- read.csv(paste0("../output/maxent/models/", timeslice, "/maxentResults.csv"), header = TRUE)
    } else if (yr == 2005){
    maxr2005 <- read.csv(paste0("../output/maxent/models/", timeslice, "/maxentResults.csv"), header = TRUE)
    } else if (yr == 2006){
    maxr2006 <- read.csv(paste0("../output/maxent/models/", timeslice, "/maxentResults.csv"), header = TRUE)
  }
}

@@

write.csv(maxrm, paste0("../output/maxent/models/", mth, "avgmaxentresults.csv"), row.names = FALSE)
```

for this bit may need to stack rasters by depth... this will need some working with the name
get unique filenames into a list
ignore the first X characters in the filename (yr_mth_) and stack based on the last bit of the filename
then do something probably with raster package

```{r avg asc layers}
asc_list <- list.files(paste0("../output/maxent/predictions/", mth), pattern = "*.asc", full.names = TRUE)
depthlayers <- data.frame(cbind(unique(stdep$ascdepths)))
names(depthlayers)[names(depthlayers) == "cbind.unique.stdep.ascdepths.."] <- "depth"
depthlayers$depth <- as.character(depthlayers$depth)

@@

for (d in 1:nrow(depthlayers)){
  dep <- depthlayers$depth[d]
  for (a in 1:length(asc_list)){
    asc <- asc_list[a]
    if (grepl(dep, asc)){
      depthlayers[d , paste0("a", colno)] <- asc
        colno <- colno+1
    }
  }
}
write.csv(depthlayers, (paste0("../output/maxent/predictions/", mth, "/asclayerbydepth.csv")), row.names = TRUE)

for (x in 1:nrow(depthlayers)){
  asclay <- depthlayers[1, ]
  asclay <- asclay[!is.na(asclay)]
  asclay <- as.data.frame(rbind(asclay))
  asclay$V1 <- as.character(asclay$V1)
  asclay$V2 <- as.character(asclay$V2)
  asclay$V3 <- as.character(asclay$V3)
  asclay$V4 <- as.character(asclay$V4)
  asclay$V5 <- as.character(asclay$V5)
  asclaydep <- asclay$V1

@@

  writeRaster(avg, (paste0("../output/maxent/predictions/", mth, "/avg_", asclaydep, ".asc")), overwrite=TRUE)
  avgplot <- plot(avg, png(paste0("../output/maxent/predictions/", mth, "/avg_", asclaydep, ".png"))) 
  dev.off()
}

>>>>

---
title: "maxent model avec xvalidation (year-based test training)"
author: "Samantha Andrews"
output: html_notebook
---

@@

```{r pre-install & load packages, include=FALSE}
packages <- c("dismo", "stringr", "rJava")
source("../src/ipak.R")
ipak(packages)
```

@@

```{r}
janvar <- c("occurrence", "year", "temp_depth", "salinity_depth", "o2_depth", "chl_surface", "nao_sample", "nao_winter")
marvar <- c("occurrence", "year", "temp_depth", "salinity_depth", "o2_depth", "chl_surface", "nao_sample", "nao_prev", "nao_winter", "amo_sample", "amo_winter")
aprvar <- c("occurrence", "year", "temp_depth", "salinity_depth", "o2_depth", "chl_surface", "nao_sample", "nao_prev", "nao_winter", "amo_sample", "amo_winter")
mayvar <- c("occurrence", "year", "temp_depth", "salinity_depth", "o2_depth", "chl_surface", "nao_sample", "nao_prev", "nao_winter", "amo_sample", "amo_winter")
junvar <- c("occurrence", "year", "temp_depth", "salinity_depth", "o2_depth", "nao_sample", "nao_prev", "nao_winter", "amo_sample", "amo_winter")
julvar <- c("occurrence", "year", "temp_depth", "salinity_depth", "o2_depth", "chl_surface", "nao_sample", "nao_prev", "nao_winter", "amo_sample", "amo_winter")
augvar <- c("occurrence", "year", "temp_depth", "salinity_depth", "o2_depth", "chl_surface", "nao_sample", "nao_prev", "nao_winter", "amo_sample", "amo_winter")
sepvar <- c("occurrence", "year", "temp_depth", "salinity_depth", "o2_depth", "chl_surface", "nao_sample", "nao_prev", "nao_winter", "amo_sample", "amo_winter")
octvar <- c("occurrence", "year", "temp_depth", "salinity_depth", "o2_depth", "nao_sample", "nao_prev", "nao_winter", "amo_sample", "amo_winter")
novvar <- c("occurrence", "year", "temp_depth", "salinity_depth", "o2_depth", "chl_surface", "nao_sample", "nao_prev", "nao_winter", "amo_sample", "amo_winter")
decvar <- c("occurrence", "year", "temp_depth", "salinity_depth", "o2_depth", "chl_surface", "nao_sample", "nao_prev", "nao_winter", "amo_sample", "amo_winter")

mthnavar_lst <- list(jan = janvar, mar = marvar, apr = aprvar, may = mayvar, jun = junvar, jul = julvar, aug = augvar, sep = sepvar, oct = octvar, nov = novvar, dec = decvar)
```

select mont
```{r month of interest -change}
mthna <- "mar"
mthno <- "3"
```

```{r subsest data by month}
prback <- subset(presback, month == mthno)
prback <- subset(prback, select = mthnavar_lst[[mthna]])
```

@@

```{r remove na vals}
prback <- na.omit(prback)
```

@@

```{r train and test on jan inc AIC for reg val}
modelmonth <- cbind(paste0(mthna ,unique(prback$year)))
aicetc <- read.csv("../data/env/AICcCalculations.csv", header = TRUE) #pre-created csv file
betavallist <- cbind(aicetc$regularization)

for (year in 1:nrow(modelmonth)){
  timeslice <- modelmonth[year] #testing timeslice
  yr <- str_sub(timeslice, -4) #the year being used for testing
  train <- subset(prback, year != yr) #training data is all years but testing
  trainpa <- train$occurrence #creates a vector of presence/background ID (1/0)
  test <-  subset(prback, year == yr) #creates the testing dataset
  testp <- subset(test, occurrence == "1") #splits the testing dataset into presences
  testp <- subset(testp, select = -c(year, occurrence)) #don't need year and occurrence for modelling
  testb <- subset(test, occurrence == "0") #splits the testing dataset into background
  testb <- subset(testb, select = -c(year, occurrence)) #don't need year and occurrence for modelling
  train  <- subset(train, select = -c(year, occurrence)) #don't need year and occurrence for modelling

@@

```{r final models plus predict}
modelmonth <- cbind(paste0(mthna, unique(prback$year)))
aicetc <- read.csv("../data/env/AICcFinalmod.csv", header = TRUE) #pre-created csv file
unlayer <- read.csv(paste0("../data/env/asc_layerlist", mthna, ".csv"), header = TRUE) #if code doesnt work put back to unlayer_yr

for (year in 1:nrow(modelmonth)){
  timeslice <- modelmonth[year] #testing timeslice
  yr <- str_sub(timeslice, -4) #the year being used for testing
  train <- subset(prback, year != yr) #training data is all years but testing
  trainpa <- train$occurrence #creates a vector of presence/background ID (1/0)
  test <-  subset(prback, year == yr) #creates the testing dataset
  testp <- subset(test, occurrence == "1") #splits the testing dataset into presences
  testp <- subset(testp, select = -c(year, occurrence)) #don't need year and occurrence for modelling
  testb <- subset(test, occurrence == "0") #splits the testing dataset into background
  testb <- subset(testb, select = -c(year, occurrence)) #don't need year and occurrence for modelling
  train  <- subset(train, select = -c(year, occurrence)) #don't need year and occurrence for modelling

@@

    for (td in 1:nrow(unlayer_yr)){
      temp_depth <- raster(unlayer_yr$temp_depth[td])
      crs(temp_depth) <- "+proj=longlat +datum=WGS84 +ellps=WGS84 +towgs84=0,0,0" 
      names(temp_depth) <- "temp_depth"
      temp_depth <- projectRaster(temp_depth, aea)
      chl_surface <- raster(unlayer_yr$chl_surface[td])
      crs(chl_surface) <- "+proj=longlat +datum=WGS84 +ellps=WGS84 +towgs84=0,0,0" 
      names(chl_surface) <- "chl_surface"
      chl_surface <- projectRaster(chl_surface, aea)
      o2_depth <- raster(unlayer_yr$o2_depth[td])
      crs(o2_depth) <- "+proj=longlat +datum=WGS84 +ellps=WGS84 +towgs84=0,0,0" 
      names(o2_depth) <- "o2_depth"
      o2_depth <- projectRaster(o2_depth, aea)
      salinity_depth <- raster(unlayer_yr$salinity_depth[td])
      crs(salinity_depth) <- "+proj=longlat +datum=WGS84 +ellps=WGS84 +towgs84=0,0,0" 
      names(salinity_depth) <- "salinity_depth"
      salinity_depth <- projectRaster(salinity_depth, aea)
      nao_sample <- raster(unlayer_yr$nao_sample[td])
      crs(nao_sample) <- "+proj=longlat +datum=WGS84 +ellps=WGS84 +towgs84=0,0,0" 
      names(nao_sample) <- "nao_sample"
      nao_sample <- projectRaster(nao_sample, aea)
      nao_winter <- raster(unlayer_yr$nao_winter[td])
      crs(nao_winter) <- "+proj=longlat +datum=WGS84 +ellps=WGS84 +towgs84=0,0,0"
      names(nao_winter) <- "nao_winter"
      nao_winter <- projectRaster(nao_winter, aea)
      stackn <- unlayer_yr$stackname[td]
      stack <- stack(temp_depth, chl_surface, o2_depth, salinity_depth, nao_sample, nao_winter)
      #stackSave(test,unlayer_yr$stackname[td])
      pred <- predict(mod, stack, file = paste0("../output/maxent/predictions/", mthna, "/", stackn, ".asc"), overwrite=TRUE, args='outputformat=cloglog') 
      prplot <- plot(pred, png(paste0("../output/maxent/predictions/", mthna, "/", stackn, ".png"))) 
      dev.off() # stops automatic saving of the plot to a png
    }
}

stdep <- do.call(rbind, stackdeplst)
write.csv(stdep, paste0("../output/maxent/predictions/", mthna, "/stack_depth.csv"), row.names = FALSE)
```

@@

```{r avg maxentReg}

for (i in 1:length(modelmonth)){
  timeslice <- modelmonth[i]
  yr <- str_sub(timeslice, -4) #the year being used for testing
  if(yr == 2003){
    aic2003 <- read.csv(paste0("../output/maxent/models/", timeslice, "/AICforMaxentReg.csv"), header = TRUE)
    } else if (yr == 2004){
    aic2004 <- read.csv(paste0("../output/maxent/models/", timeslice, "/AICforMaxentReg.csv"), header = TRUE)
    } else if (yr == 2005){
    aic2005 <- read.csv(paste0("../output/maxent/models/", timeslice, "/AICforMaxentReg.csv"), header = TRUE)
    } else if (yr == 2006){
    aic2006 <- read.csv(paste0("../output/maxent/models/", timeslice, "/AICforMaxentReg.csv"), header = TRUE)
  }
}

@@

write.csv(avgAIC, paste0("../output/maxent/models/", mthna, "avgAIC.csv"), row.names = FALSE)
```

```{r avg maxres}

for (i in 1:length(modelmonth)){
  timeslice <- modelmonth[i]
  yr <- str_sub(timeslice, -4) #the year being used for testing
  if(yr == 2003){
    maxr2003 <- read.csv(paste0("../output/maxent/models/", timeslice, "/maxentResults.csv"), header = TRUE)
    } else if (yr == 2004){
    maxr2004 <- read.csv(paste0("../output/maxent/models/", timeslice, "/maxentResults.csv"), header = TRUE)
    } else if (yr == 2005){
    maxr2005 <- read.csv(paste0("../output/maxent/models/", timeslice, "/maxentResults.csv"), header = TRUE)
    } else if (yr == 2006){
    maxr2006 <- read.csv(paste0("../output/maxent/models/", timeslice, "/maxentResults.csv"), header = TRUE)
  }
}

@@

write.csv(maxrm, paste0("../output/maxent/models/", mthna, "avgmaxentresults.csv"), row.names = FALSE)
```

for this bit may need to stack rasters by depth... this will need some working with the name
get unique filenames into a list
ignore the first X characters in the filename (yr_mthna_) and stack based on the last bit of the filename
then do something probably with raster package

```{r avg asc layers}
asc_list <- list.files(paste0("../output/maxent/predictions/", mthna), pattern = "*.asc", full.names = TRUE)
depthlayers <- data.frame(cbind(unique(stdep$ascdepths)))
names(depthlayers)[names(depthlayers) == "cbind.unique.stdep.ascdepths.."] <- "depth"
depthlayers$depth <- as.character(depthlayers$depth)

@@

for (d in 1:nrow(depthlayers)){
  dep <- depthlayers$depth[d]
  for (a in 1:length(asc_list)){
    asc <- asc_list[a]
    if (grepl(dep, asc)){
      depthlayers[d , paste0("a", colno)] <- asc
        colno <- colno+1
    }
  }
}
write.csv(depthlayers, (paste0("../output/maxent/predictions/", mthna, "/asclayerbydepth.csv")), row.names = TRUE)

for (x in 1:nrow(depthlayers)){
  asclay <- depthlayers[x, ]
  asclay <- asclay[!is.na(asclay)]
  asclay <- as.data.frame(rbind(asclay))
  asclay$V1 <- as.character(asclay$V1)
  asclay$V2 <- as.character(asclay$V2)
  asclay$V3 <- as.character(asclay$V3)
  asclay$V4 <- as.character(asclay$V4)
  asclay$V5 <- as.character(asclay$V5)
  asclaydep <- asclay$V1

@@

  writeRaster(avg, (paste0("../output/maxent/predictions/", mthna, "/avg_", asclaydep, ".asc")), overwrite=TRUE, args='outputformat=cloglog')
  avgplot <- plot(avg, png(paste0("../output/maxent/predictions/", mthna, "/avg_", asclaydep, ".png"))) 
  dev.off()
}

ascdepth_list <- list.files(paste0("../output/maxent/predictions/", mthna), glob2rx(pattern = "avg_*.asc"), full.names = TRUE)

asc120  <- raster(paste0("../output/maxent/predictions/", mthna, "/avg_120.asc"))
asc41.18 <- raster(paste0("../output/maxent/predictions/", mthna, "/avg_41.18.asc"))
asc1.55586 <- raster(paste0("../output/maxent/predictions/", mthna, "/avg_1.55586.asc"))
asc1045.85 <- raster(paste0("../output/maxent/predictions/", mthna, "/avg_1045.85.asc"))
asc108.03 <- raster(paste0("../output/maxent/predictions/", mthna, "/avg_108.03.asc"))
asc11.7737 <- raster(paste0("../output/maxent/predictions/", mthna, "/avg_11.7737.asc"))
asc1151.99 <- raster(paste0("../output/maxent/predictions/", mthna, "/avg_1151.99.asc"))
asc1265.86 <- raster(paste0("../output/maxent/predictions/", mthna, "/avg_1265.86.asc"))
asc13.991 <- raster(paste0("../output/maxent/predictions/", mthna, "/avg_13.991.asc"))
asc133.076 <- raster(paste0("../output/maxent/predictions/", mthna, "/avg_133.076.asc"))
asc1387.38 <- raster(paste0("../output/maxent/predictions/", mthna, "/avg_1387.38.asc"))
asc147.406 <- raster(paste0("../output/maxent/predictions/", mthna, "/avg_147.406.asc"))
asc16.5253 <- raster(paste0("../output/maxent/predictions/", mthna, "/avg_16.5253.asc"))
asc163.165 <- raster(paste0("../output/maxent/predictions/", mthna, "/avg_163.165.asc"))
asc180.55 <- raster(paste0("../output/maxent/predictions/", mthna, "/avg_180.55.asc"))
asc19.4298 <- raster(paste0("../output/maxent/predictions/", mthna, "/avg_19.4298.asc"))
asc199.79 <- raster(paste0("../output/maxent/predictions/", mthna, "/avg_199.79.asc"))
asc2.66768 <- raster(paste0("../output/maxent/predictions/", mthna, "/avg_2.66768.asc"))
asc22.7576 <- raster(paste0("../output/maxent/predictions/", mthna, "/avg_22.7576.asc"))
asc221.141 <- raster(paste0("../output/maxent/predictions/", mthna, "/avg_221.141.asc"))
asc244.891 <- raster(paste0("../output/maxent/predictions/", mthna, "/avg_244.891.asc"))
asc26.5583 <- raster(paste0("../output/maxent/predictions/", mthna, "/avg_26.5583.asc"))
asc271.356 <- raster(paste0("../output/maxent/predictions/", mthna, "/avg_271.356.asc"))
asc3.85628 <- raster(paste0("../output/maxent/predictions/", mthna, "/avg_3.85628.asc"))
asc30.8746 <- raster(paste0("../output/maxent/predictions/", mthna, "/avg_30.8746.asc"))
asc300.888 <- raster(paste0("../output/maxent/predictions/", mthna, "/avg_300.888.asc"))
asc333.863 <- raster(paste0("../output/maxent/predictions/", mthna, "/avg_333.863.asc"))
asc35.7402 <- raster(paste0("../output/maxent/predictions/", mthna, "/avg_35.7402.asc"))
asc370.689 <- raster(paste0("../output/maxent/predictions/", mthna, "/avg_370.689.asc"))
asc411.794 <- raster(paste0("../output/maxent/predictions/", mthna, "/avg_411.794.asc"))
asc457.626 <- raster(paste0("../output/maxent/predictions/", mthna, "/avg_457.626.asc"))
asc47.2119 <- raster(paste0("../output/maxent/predictions/", mthna, "/avg_47.2119.asc"))
asc5.14036 <- raster(paste0("../output/maxent/predictions/", mthna, "/avg_5.14036.asc"))
asc508.64 <- raster(paste0("../output/maxent/predictions/", mthna, "/avg_508.64.asc"))
asc53.8506 <- raster(paste0("../output/maxent/predictions/", mthna, "/avg_53.8506.asc"))
asc565.292 <- raster(paste0("../output/maxent/predictions/", mthna, "/avg_565.292.asc"))
asc6.54303 <- raster(paste0("../output/maxent/predictions/", mthna, "/avg_6.54303.asc"))
asc61.1128 <- raster(paste0("../output/maxent/predictions/", mthna, "/avg_61.1128.asc"))
asc628.026 <- raster(paste0("../output/maxent/predictions/", mthna, "/avg_628.026.asc"))
asc69.0217 <- raster(paste0("../output/maxent/predictions/", mthna, "/avg_69.0217.asc"))
asc697.259 <- raster(paste0("../output/maxent/predictions/", mthna, "/avg_697.259.asc"))
asc77.6112 <- raster(paste0("../output/maxent/predictions/", mthna, "/avg_77.6112.asc"))
asc773.368 <- raster(paste0("../output/maxent/predictions/", mthna, "/avg_773.368.asc"))
asc8.09252 <- raster(paste0("../output/maxent/predictions/", mthna, "/avg_8.09252.asc"))
asc856.679 <- raster(paste0("../output/maxent/predictions/", mthna, "/avg_856.679.asc"))
asc86.9294 <- raster(paste0("../output/maxent/predictions/", mthna, "/avg_86.9294.asc"))
asc9.82275 <- raster(paste0("../output/maxent/predictions/", mthna, "/avg_9.82275.asc"))
asc947.448 <- raster(paste0("../output/maxent/predictions/", mthna, "/avg_947.448.asc"))
asc97.0413 <- raster(paste0("../output/maxent/predictions/", mthna, "/avg_97.0413.asc"))

stackavg <- stack(asc120, asc41.18, asc1.55586, asc1045.85, asc108.03, asc11.7737, asc1151.99, asc1265.86, asc13.991, asc133.076, asc1387.38, asc147.406, asc16.5253, asc163.165, asc180.55, asc19.4298, asc199.79, asc2.66768, asc22.7576, asc221.141, asc244.891, asc26.5583, asc271.356, asc3.85628, asc30.8746, asc300.888, asc333.863, asc35.7402, asc370.689, asc411.794, asc457.626, asc47.2119, asc5.14036, asc508.64, asc53.8506, asc565.292, asc6.54303, asc61.1128, asc628.026, asc69.0217, asc697.259, asc77.6112, asc773.368, asc8.09252, asc856.679, asc86.9294, asc9.82275, asc947.448, asc97.0413)

sum <- calc(stkasc, fun = sum)
avg <- calc(stkasc, fun = mean)
  writeRaster(avg, (paste0("../output/maxent/predictions/", mthna, "/avg_", mthna, ".asc")), overwrite=TRUE)
  avgplot <- plot(avg, png(paste0("../output/maxent/predictions/", mthna, "/avg_", mthna, ".png"))) 
  dev.off()
